Hydras \& Co.

### 2022-05-09 doc/gaia-chapter.tex
corrections in tex files

Some constructions of \HydrasLib were (to our knowledge) not implemented in \gaia yet. For instance, commutative (``Hessenberg'') addition, canonical sequences and Ketonen-Solovay machinery (Chapters~\ref{chap:T1}, \ref{chap:ketonen} and \ref{chap:alpha-large}). In order not to copy long proofs, we chose to
\emph{derive} several constructions from \HydrasLib into \gaia's world, and rewrite \HydrasLib statements in order to make them \gaia-compatible.

>>>>

Some constructions of \HydrasLib were (to our knowledge) not implemented in \gaia yet, for instance, commutative (``Hessenberg'') addition, canonical sequences and Ketonen-Solovay machinery (Chapters~\ref{chap:T1}, \ref{chap:ketonen} and \ref{chap:alpha-large}). In order not to copy long proofs, we chose to
\emph{derive} several constructions from \HydrasLib into \gaia's world, and rewrite \HydrasLib statements in order to make them \gaia-compatible.
